Different forms of uncertainty differently affect the evolution of social learning

### 2022-08-01 Figures/supplement/fullMeanPrevNetPayoffs.tex
full revision with N=1000 data

\usepackage{geometry}
\geometry{
paperwidth=8in,
paperheight=6.25in,
margin=0.25in
}

@@

\begin{document}

    \begin{minipage}{3.75in}
      \centering
      {\hspace{5.25em}\huge $B = 2$}
    \end{minipage}%
    \begin{minipage}{3.75in}
      \centering
      {\hspace{2.0em}\huge $B = 10$}
    \end{minipage}~\\

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.1$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
    \end{minipage}\noindent\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
    \end{minipage}~\\[0.5em]

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.45$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
        \\[-2.75em]
        \begin{center}
          {\hspace{3.25em} \huge $\quad u$}
      \end{center}
        \end{minipage}\noindent\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
      \\[-2.75em]
      \begin{center}
        {\huge $\quad u$}
      \end{center}
    \end{minipage}
\end{document}

>>>>

\usepackage{geometry}
\geometry{
paperwidth=12in,
paperheight=10in,
margin=0.25in
}

@@

\begin{document}
\begin{tikzpicture}
      \draw[->,thick] (-.1,0)--(1.15,0) node[above]
        {\huge $B$};
        % {Number of behaviors $B$};
      \draw[->,thick] (0,.1)--(0,-1.15) node[below]
        {\huge $\pilow$};
        % {Low payoff frequency $\pilow$};
	  \end{tikzpicture}~\\[-2em]

    \begin{minipage}{3.75in}
      \centering
      {\hspace{5.25em}\huge $B = 2$}
    \end{minipage}%
    \begin{minipage}{3.75in}
      \centering
      {\hspace{1.0em}\huge $B = 4$}
    \end{minipage}%
    \begin{minipage}{3.75in}
      \centering
      {\hspace{2.0em}\huge $B = 10$}
    \end{minipage}~\\

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.1$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
    \end{minipage}\noindent\hspace{1.25em}
	\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
    \end{minipage}\noindent
	\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
    \end{minipage}~\\[0.5em]

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.45$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
	\end{minipage}\noindent\hspace{1.25em}
	\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
    \end{minipage}\noindent
	\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
    \end{minipage}~\\[0.5em]

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.8$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
        \\[-2.75em]
        \begin{center}
          {\hspace{3.25em} \huge $\quad u$}
      \end{center}
	  \end{minipage}\noindent\hspace{1.25em}
		\begin{minipage}{3.75in}%
		  \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
		  \\[-2.75em]
	  \begin{center}
        {\huge $\quad u$}
      \end{center}
    \end{minipage}
	\begin{minipage}{3.75in}%
		  \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
		  \\[-2.75em]
	  \begin{center}
        {\huge $\quad u$}
      \end{center}
	\end{minipage}
\end{document}
